---
title: "Final_Code"
author: "New_Group_1"
date: "2024-10-01"
output: html_document
---


## 0 Initialization: 

```{r setup, include=FALSE}

setwd(here::here())   # Setup work path at'here'
rm(list = ls())       # Clear all variables in the environment.

```

## 1 Read the text file

```{r echo=TRUE, eval=TRUE, message=FALSE}

a <- scan("4300-0.txt",what="character",skip=73,nlines=32858-73,
          fileEncoding="UTF-8")
a <- gsub("_(","",a,fixed=TRUE)                   # remove "_("

```

## 2 Pre-Processing (split punctuation mark with words)

# 2.1. Define the [split_punct] function.

The specific steps are as follows:

Step 1: Give the input parameters: [text_vector] a text vector; [punctuation] a punctuation mark in the form of a string;  <br>
Step 2: Find the indices of the punctuation in text vector -> [punctuation_indices];  <br>
Step 3: Creat a new vector to contain the text and punctuation -> [new_vector];  <br>
Step 4: Iterate over the [punctuation_indices] variable;  <br>
Step 5: According to indecies, copy the element in [text_vector] to [new_vector] in which leave a "NA" between the gap;  <br>
Step 6: Ensure the copy procedure is complete (after the last element in [indecies], it may have a fragment of vector);  <br>
Step 7: Find the new indices of the [punctuation] in [new_vector] -> [punct_indices_1];  <br>
Step 8: Remove the [punctuation] in [new_vector];  <br>
Step 9: Replace the NA with [punctuation].  <br>

```{r echo=TRUE, eval=TRUE, message=FALSE}

split_punct <- function(text_vector, punctuation){

  punctuation_indices <- grep(punctuation, text_vector, fixed = TRUE)   # Find the indices of the punctuation in text vector

  new_vector_length <- length(text_vector) + length(punctuation_indices)
  new_vector <- vector("character", new_vector_length)                  # Creat a new vector to contain the text and punctuation

  last_index <- 1
  start_index <- 1

  for (index in punctuation_indices) {                                  # Iterate over the [punctuation_indices] variable

    new_vector[last_index:(last_index + (index - start_index))] <- text_vector[start_index:index]
    last_index <- last_index + (index - start_index + 1)
    new_vector[last_index] <- NA
    last_index <- last_index + 1
    start_index <- index + 1                                            # According to indecies, copy the element in [text_vector] to [new_vector] in which leave a "NA" between the gap
  }

  if (start_index <= length(text_vector)) {                             # Ensure the copy procedure is complete (after the last element in [indecies], it may have a fragment of vector)
    new_vector[last_index:(last_index + (length(text_vector) - start_index + 1) - 1)] <- text_vector[start_index:length(text_vector)]
  }
  
  punct_indices_1 <- grep(punctuation, new_vector, fixed = TRUE)        # Find the new indices of the [punctuation] in [new_vector]
  new_vector <- gsub(punctuation, "", new_vector, fixed=TRUE)           # Remove the [punctuation] in [new_vector]
  new_vector[punct_indices_1 + 1] <- punctuation                        # Replace the NA with [punctuation].

  return(new_vector)
}

```

# 2.2 Execute [split_punct] function.

```{r echo=TRUE, eval=TRUE, message=FALSE}

punctuation_vector <- c(",", ".", ";", "!", ":", "?")

a1 <- a

for (punc in punctuation_vector){
  a1 <- split_punct(a1, punc)
}

# saveRDS(a1, file = "word_vector1.rds")
# a1 <- readRDS("word_vector1.rds")

```

## 3 Find Top ≈1000 words of occurrences & creat common word vector

The specific steps are as follows:

Step 1: Convert text vector [a1] to lower case;   <br>
Step 2: unique [a1] -> [uni];    <br>
Step 3: tabulate [uni] -> [occurrences];    <br>
Step 4: Choose a suitable threshold, and we find when the threshold is 26, the size of common word vector is 1005;    <br>

```{r echo=TRUE, eval=TRUE, message=FALSE}

a1 <- tolower(a1)                                     # Convert text vector [a1] to lower case
uni <- unique(a1)                                     # unique [a1]

cal_occurrences <- match(a1, uni)

occurrences <- tabulate(cal_occurrences)              # tabulate [uni]

freq <- 26                                            # Choose a suitable threshold, and we find when the threshold is 26, the size of common word vector is 1005

b <- uni[which(occurrences > freq)]                   # size of b = 1005

occurrences_b <- occurrences[which(occurrences > freq)]

print(paste("Length of common word vector: ", length(b)))

```

## 4 Build the matrices of word token sequences

Choose a [mlag] means determine a scan-width.

The 'scan' means:

After match function, vector [tmp] can be [1, 2, 3, 4, 5, 6, 7, 8, 9]

For example:

If the [mlag] = 3, [M] will be:

[1, 2, 3
 2, 3, 4
 3, 4, 5
 4, 5, 6
 5, 6, 7
 6, 7, 8
 7, 8, 9]

where the first column stand for itself (as indices in original text vector), the follow columns is their immediate text

```{r echo=TRUE, eval=TRUE, message=FALSE}

tmp <- match(a1, b)

mlag <- 4
n <- length(a1)

M <- matrix(NA, nrow = (n - mlag), ncol = (mlag + 1))

for (i in 1:(n - mlag)) {
  M[i, ] <- tmp[i:(mlag + i)]
}

```

## 5 Simulate nw-word sections from our model

# 5.1 Generate first word

```{r echo=TRUE, eval=TRUE, message=FALSE}

nw = 50

M[is.na(M)] <- 0

indices <- grepl("^[A-Za-z]+$", a1)                  # Avoid the first word being a punctuation mark
words <- a1[indices]
freqs <- tmp[indices]
freqs[is.na(freqs)] <- 0

set.seed(2)
start_word <- sample(words, 1, prob = freqs)         # Generate first word in random (according to their frequencies)

sentence <- start_word

```

# 5.2 Nested loops to generate the sentences

The surrounding loop is to make sure the 'generate action' will take place (nw - 1) times

The inner loop is the 'generate action'. It work as follow:

Step 1: Find the last word [start_word] (which will be cover at the end of inner loop);  <br>
Step 2: Find the indices of [start_word] in origin text vector [a1] -> [indices];  <br>
Step 3: Select the corresponding [pth: mlag] vector (the mlag + 1) column -> [freqs];  <br>
Step 4: if the [freqs] is a all-zero vector, then degenerate to (p-1)th model;  <br>
Step 5: else, select a word form uni[freqs];  <br>
Step 6: if all pth, (p-1)th, ..., 1th models are failed, choose another word in random;  <br>

```{r echo=TRUE, eval=TRUE, message=FALSE}

for (i in 2:nw) {                                # The surrounding loop is to make sure the 'generate action' will take place (nw - 1) times
  select_word <- ""
  
  for (j in mlag:1) if (i>j) { ## skip lags too long for current i;      The inner loop is the 'generate action'.
    indices <- which(a1[1: (n - mlag)] == start_word)                 # Find the last word [start_word] (which will be cover at the end of inner loop)
    freqs = M[indices, j + 1]             # Find the indices of [start_word] in origin text vector [a1] & Select the corresponding [pth: mlag] vector (the mlag + 1) column
    
    if (all(freqs == 0)){                 # if the [freqs] is a all-zero vector, then degenerate to (p-1)th model
      next
    }else{                                # else, select a word form uni[freqs]
      select_word <- sample(uni[freqs], 1)
      break
    }
  }
  
  if (select_word == ""){                 # if all pth, (p-1)th, ..., 1th models are failed, choose another word in random
    select_word <- sample(a1, 1, prob = tmp)
  }
  
  sentence <- paste(sentence, select_word, sep = " ")
  start_word <- select_word
}

cat("\n", sentence, "\n", "\n")

```

## Refine the output. (Last 3 marks)

Convert the first letter of the first word to upper form.

Remove Spaces before punctuation marks.

Convert the first letter of the first word after punctuation mark to upper form.

Add '.' after the last word

```{r echo=TRUE, eval=TRUE, message=FALSE}

sentence1 <- sub("^(\\w)", "\\U\\1", sentence, perl = TRUE)           # Convert the first letter of the first word to upper form.

sentence1 <- gsub("\\s+([.,!?])", "\\1", sentence1)                   # Remove Spaces before punctuation marks.

words <- unlist(strsplit(sentence1, " "))                             # Convert the first letter of the first word after punctuation mark to upper form.
for (i in 1:length(words)) {
  if (i > 1 && nchar(words[i - 1]) > 0 && grepl("[.,!?]", substring(words[i - 1], nchar(words[i - 1]), nchar(words[i - 1])))) {
    words[i] <- paste0(toupper(substring(words[i], 1, 1)), substring(words[i], 2))
  }
}
sentence1 <- paste(words, collapse = " ")
sentence1 <- paste(sentence1, ".", sep = "")                          # Add '.' after the last word

cat("\n", "Origin Version: ", sentence, "\n", "\n")
cat("\n", "Refined Version: ", sentence1, "\n", "\n")


```



